### 2015-05-19 writing/SNLI paper/entailment_eval.tex
Paper update.

\subsection{Sentence embeddings and NLI}\label{sentence-embedding}
\input{model_structure_fig.tex}

Since our goal is to evaluate the quality of the single sentence representations in our model, we train an entailment classifier that has access only to the output of our sentence representation model, and not to any of the word or phrase representations that it used. We encourage future users of this corpus to evaluate their models in this way when possible. Our classifier is simply a stack of three 100d $\tanh$ layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the representation model itself.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train (3-Class)}  & \b{Test (3-Class)}\\
 & \t{Acc.} & \t{Acc.} \\
\hline
\t{Sum of words}            & \t{} & \t{} \\
\t{RNN}            & \t{} & \t{} \\
\t{LSTM RNN}            & \t{75?} & \t{72?} \\
\t{TreeRNN}            & \t{} & \t{} \\
\t{TreeRNTN}            & \t{58?} & \t{56?} \\
\t{LSTM TreeRNN}            & \t{72?} & \t{69?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy on the 2-class and 3-class SNLI dataset, as well as precision/recall
  on the 2-class task to allow for comparision with the RTE systems.
Ablation studies are reported for removing bigram features and all lexical
  features.
\todo{numbers are approx.}
}
\end{table}

\subsection{Results}

>>>>

\subsection{Sentence embeddings and NLI}\label{sentence-embedding}

SNLI is uniquely suitable for training neural network models that produce vector representations of sentence meaning. In this section, we compare the performance of six such models on SNLI. 
In order to best evaluate the strengths of these six models at producing informative representations, we use sentence embedding as an intermediate step in the NLI classification task: each model most produce vector representation of each of the two sentences without using any context from the other sentence, and the two resulting vectors are then passed to a neural network classifier which predicts the label for the pair. This choice allows us to focus on evaluating the ability of existing models to produce representations that fully capture sentence meaning, at the possible cost of excluding from consideration neural models for NLI that directly compare the two inputs at the word or phrase level.

\input{model_structure_fig.tex}

Our neural network classifier, depicted in Fig.~\ref{modelstructure} is simply a stack of three 100d $\tanh$ layers, with the bottom layer taking the concatenated sentence representations as input and the top layer feeding a softmax classifier, all trained jointly with the representation model itself.

We test six sentence representation models, each set to use 50d word and phrase embeddings. Our baseline model in this experiment simply sums the embeddings of the word in each sentence. Next, we experiment with two recurrent models: a plain RNN, and a one-layer LSTM RNN \cite{hochreiter1997long}. Finally, we experiment with three tree-structured models: a plain TreeRNN \cite{socher2011semi}, a tensor-parameterized TreeRNTN \cite{socher2013acl1}, and a TreeLSTM \cite{tai2015improved}.

The word embeddings for all of the moedels are initialized the 200d reference GloVe vectors \cite{pennington2014glove} and fine tuned. In addition, all of the models use an additional $\tanh$ neural network layer to map these 200d embeddings into the 50d working space. All of the models are randomly initialized using standard techniques and trained using AdaDelta \cite{zeiler2012adadelta} minibatch SGD until performance on the development set stops improving. We applied L2 regularization to all models, manually tuning the strength coefficient $\lambda$ for each. All models were reimplemented in a common framework for this paper, and the implementations will be made available at publication time.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{Sum of words}            & \t{} & \t{} \\
\t{RNN}            & \t{} & \t{} \\
\t{LSTM RNN}            & \t{75?} & \t{72?} \\
\t{TreeRNN}            & \t{} & \t{} \\
\t{TreeRNTN}            & \t{58?} & \t{56?} \\
\t{LSTM TreeRNN}            & \t{72?} & \t{69?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the SNLI training and test sets for each model.
\todo{Replace with final numbers}
}
\end{table}

### 2015-05-19 writing/SNLI paper/model_structure_fig.tex
Pre-lunch paper update.
Paper update.

\begin{figure}[tp]
  \centering

 \begin{tikzpicture}
    \def\dx{19pt}
    \def\dy{29pt}

    \tikzstyle{label}=[text width=40mm,align=center]    
    \tikzstyle{softmax}=[fill=red!40,text width=40mm,align=center]
    \tikzstyle{preclass}=[fill=orange!40,text width=50mm,align=center]
    \tikzstyle{e}=[fill=green!40,text width=25mm,align=center]
    \tikzstyle{m}=[fill=blue!40,text width=34mm,align=center]

@@

  \end{tikzpicture}

        \caption{The standard model structure used for entailment evaluation.}
  \label{sample-figure}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
\scalebox{0.85}{
 \begin{tikzpicture}
    \def\dx{21pt}
    \def\dy{29pt}

    \tikzstyle{label}=[text width=40mm,align=center]    
    \tikzstyle{softmax}=[fill=red!40,text width=40mm,align=center]
    \tikzstyle{preclass}=[fill=orange!40,text width=50mm,align=center]
    \tikzstyle{e}=[fill=green!40,text width=25mm,align=center]
    \tikzstyle{m}=[draw=black,text width=38mm,align=center]

@@

  \end{tikzpicture}}

        \caption{The common classification architecture used in all NLI evaluations: for each model evaluated in Table~\ref{tab:nnresults}, two identical copies of the model are run with the two sentences as input, and their outputs are used as the two 50d inputs shown here.}
  \label{modelstructure}
\end{figure}

### 2015-05-19 writing/SNLI paper/transfer.tex
Paper update.

\subsection{SNLI and transfer learning}

>>>>

\section{SNLI and transfer learning}

We argue that for a sentence representation to provide the information necessary to reliably perform NLI classification, it must contain a faithful and thorough description of the sentence's meaning. This claim has a readily testable consequence: the knowledge that a representation learning system learns when it is trained on SNLI should transfer well to any other task that involves understanding sentence meaning. To test this, we perform transfer learning experiments on four other tasks, in which models are initialized using the parameters of a model trained on  on SNLI (as in \S\ref{sentence-embedding}) and then trained to convergence on the target tasks.
